\singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}

### 2021-12-20 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
Cap letters in supp to match the journal formattin of PNAS

rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.10) 
rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.10)

rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.10)
rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.10)

rpart.plot(tree_3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.10) 
rpart.plot(tree3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.10)

@@

theme_ms <- function(base_size=10, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(1.3)),
           axis.text=element_text(size = rel(1.1), color = "black"),
           panel.border=element_rect(color="black",size=1.2),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           legend.position = "none",
           plot.title = element_text(face = "bold",size = rel(1.45)),
           plot.subtitle = element_text(face = "bold",size = rel(1.3))
     ))
}

@@

breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
               label = .group)) +theme_minimal()+
  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

@@

comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

@@

lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")

@@

lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")

@@

shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")

>>>>

rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)

rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)

rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)

@@

theme_ms <- function(base_size=10, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(1.3)),
           axis.text=element_text(size = rel(1.1), color = "black"),
           panel.border=element_rect(color="black",size=1.2),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           legend.position = "none",
           plot.title = element_text(face = "bold",size = rel(1.55)),
           plot.subtitle = element_text(face = "bold",size = rel(1.4))
     ))
}

@@

breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
               label = .group)) +theme_minimal()+
  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
  theme(plot.title = element_text(hjust=0.5, size=25, face="bold"))+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
  theme(plot.title = element_text(hjust=0.5,size=25, face="bold") )+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

@@

comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

@@

lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")

@@

lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")

@@

shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")
